### 2023-02-07 writing/manuscript.Rmd
Adding data_downloader script and ensuring rmd knits

country_non_unique<- country %>% 
  count(language) %>%
  filter(n !=1) %>%
  pull(language)

@@

kable(TableS1, booktab = T, linesep = NULL, longtable = T, escape = F) %>%
  kable_styling(font_size = 6.5,
                 position = "center") %>%
  column_spec(6, width = "12em")  %>% 
  footnote(general = "The languages studied here, with sample sizes, largest-sample-size country, and the source of the language classification. Abbreviations: WALS (The world atlas of language structures), LAPSyD (Lyon-Albuquerque phonological systems database). *WALS classified as simple tone.",
           general_title = "Table S1.",
           footnote_as_chunk = TRUE,
           title_format = "bold",
           escape = FALSE,
           threeparttable = TRUE)
```

>>>>

country_non_unique <- country %>% 
  count(language) %>%
  filter(n !=1) %>%
  pull(language)

@@

kable(TableS1, booktab = T, linesep = NULL, longtable = T, escape = F) %>%
  kable_styling(font_size = 6.5,
                 position = "center") %>%
  footnote(general = "The languages studied here, with sample sizes, largest-sample-size country, and the source of the language classification. Abbreviations: WALS (The world atlas of language structures), LAPSyD (Lyon-Albuquerque phonological systems database). *WALS classified as simple tone.",
           general_title = "Table S1.",
           footnote_as_chunk = TRUE,
           title_format = "bold",
           escape = FALSE,
           threeparttable = TRUE)
```
